How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in \textit{Emys marmorata} (Testudinoidea, Emydidae).

### 2013-08-08 documents/turtle_paper.tex
results updated completely. some intro work. grow turtle section.

\section{Results}
\subsection{Geometric morphometrics}
The results of the PCA of the total dataset of \textit{E. marmorata} pastral landmarks configurations demonstrates no clear or obvious groupings (Fig. \ref{fig:pca}). The first three PCs, which represent 45.2924805932624\% of the total variation, are a cloud of points with no structure. Additionally, individual landmark variation is mostly circular around each landmark with some more elliptical variation observed along some midline landmarks and the most lateral landmark (Fig. \ref{fig:pca}). However, it is important to note that Procustes based superimposition attempts to evenly distribute variance around the mean landmark \citep{Zelditch2004} and this observation should be considered cursory at best.

The first two PCs appear to describe variation in lateral plastral shape, from a very pointed medial edge to a much more rounded and blunt edge (Fig. \ref{fig:pc_var}). Landmark 10 (Fig. \ref{fig:plastra}), which appears to be the most variable along this axis (Fig. \ref{fig:pca} and \ref{fig:pc_var}), is positioned on the bridge between the plastron and the carapace. Over ontogeny, this is an area that deepens dorsoventrally and when the plastron was projected into two dimensions this it created the effect of mediolateral movement.
Additional variation along the second PC appears to be characterized by variation in anterior and posterior landmarks along the medial edge of the plastron.

@@

% multinomial logistic regression model
The AICc best multinomial logistic regression model for three of the four classification schemes include the first 9 PCs as features (Tables \ref{tab:mod_sel_1}, \ref{tab:mod_sel_2}, and \ref{tab:mod_sel_3}). The second molecularly based classification hypothesis includes all 10 PCs predictors (Tables \ref{tab:mod_sel_4}).
The \(\Delta\)AICc values between the optimal and second best model range from 1.1782 for the first morphological based classification hypothesis to 26.5107 for the second molecular based classification hypothesis (Tables \ref{tab:mod_sel_1},\ref{tab:mod_sel_2},\ref{tab:mod_sel_3}, and \ref{tab:mod_sel_4}). The first 9 PCs describe 83.2255838908058\% of total variation in plastral shape, while the first 10 PCs describe 0\% of the variation.

While the \(\Delta\)AICc value between the optimal and second best model for the first morphological and first molecular based classification hypothesis was within the range to be considered equally optimal \citep{Burnham2002a}, for this analysis we chose to use only the AICc best model. While AICc values can not be compared between models with different responses \citep{Burnham2002a}, we interpret the fact that the optimal model for three of the classification schemes having the same number of predictors and the fact that the \(\Delta\)AICc best model in these cases is the simpler mode as reasons to use only the AICc best model for all cases. 
Additionally, by using a single model for all classification schemes, this limits the number of comparisons between the bootstrap resampled distributions of the AUC values for the testing dataset (see below).

@@

The selected number of features in the final random forest model for each classification scheme varied as much as the multinomial logistic regression models, ranging from 9 for the second morphological based classification hypothesis and both molecular based classification hypotheses to 10 for the first morphological based classification hypothesis (Fig. \ref{fig:roc}).

@@

The first two most important features describe different aspects of variation (Fig. \ref{fig:imp_var}). The third and most important PC describes variation roundedness of the medial portion of the plastron, both the anterior and posterior portions of the plastron. Additionally, the relative position of the landmarks along the midline. This PC represents 12.1948\% of total variation. The second and second most important PC is described above and principally described variation in landmarks along the medial and anterior edge of the plastron. This PC represents 12.7794\% of total variation. The major variations along these axes correspond well to the differences between the mean shape of each class (Fig. \ref{fig:mean_shape}) where major class differences seem based on the relative ballooning or shrinking of the anterior and posterior portions of the plastron together.

The relative risk values for classification from the multinomial logistic regression model, based on the three most important PCs, demonstrate that individual axes contribute differently to classification and that given multiple features the odds of determining the correct classification increase (Fig. \ref{fig:rel_risk}). The first most important axis contributes strongly to classifying both the western and southern groups while changes along the second most important axes contribute very little to increasing the odds of classification for all but the eastern group. This is observable from the class histograms of PC 2 (Fig. \ref{fig:imp_var}). Changes along the first and third most important axes contribute more obviously to increasing the odds of correctly identifying the class of an observation, a result that is observable in both the relative risk (Fig. \ref{fig:rel_risk}) and the different class histograms of the PCs (Fig. \ref{fig:imp_var}).

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width = \textwidth]{figure/pc_var}
  \caption{Landmark variation along the first two PCs of the Procrustes superimposed ``half'' plastral landmarks. The first row corresponds to variation along the first PC, while the second row corresponds to the second PC. The left most column represents the observation with the highest eigenscore along that PC, while the right most column represents the observation with the lowest eigenscore. The middle column, for both rows, is the mean plastral shape for all observations. The first PC represents 20.3183\% of the total variation in plastral shape while PC represents 12.7794\% of the variance.}
  \label{fig:pc_var}
\end{figure}

@@

\begin{sidewaystable}
  \centering
% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Wed Aug  7 17:21:25 2013
{\small
\begin{tabular}{lllllllllllrrrrr}
  \hline
(Intercept) & PC1 & PC2 & PC3 & PC4 & PC5 & PC6 & PC7 & PC8 & PC9 & PC10 & df & logLik & AICc & delta & weight \\ 
  \hline
+ & + & + & + & + & + & + & + & + & + &  & 20.00 & -250.00 & 542.26 & 0.00 & 0.64 \\ 
  + & + & + & + & + & + & + & + & + & + & + & 22.00 & -248.35 & 543.43 & 1.18 & 0.36 \\ 
  + & + & + & + & + & + & + & + &  &  &  & 16.00 & -261.94 & 557.33 & 15.07 & 0.00 \\ 
  + & + & + & + & + & + & + & + & + &  &  & 18.00 & -259.99 & 557.82 & 15.56 & 0.00 \\ 
  + & + & + & + & + & + & + &  &  &  &  & 14.00 & -275.68 & 580.48 & 38.22 & 0.00 \\ 
  + & + & + & + & + & + &  &  &  &  &  & 12.00 & -281.10 & 587.03 & 44.77 & 0.00 \\ 
  + & + & + & + & + &  &  &  &  &  &  & 10.00 & -305.55 & 631.68 & 89.43 & 0.00 \\ 
  + & + & + & + &  &  &  &  &  &  &  & 8.00 & -318.48 & 653.34 & 111.09 & 0.00 \\ 
  + & + & + &  &  &  &  &  &  &  &  & 6.00 & -344.14 & 700.49 & 158.24 & 0.00 \\ 
  + & + &  &  &  &  &  &  &  &  &  & 4.00 & -346.80 & 701.71 & 159.45 & 0.00 \\ 
   \hline
\end{tabular}
}

@@

\begin{sidewaystable}
  \centering
% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Wed Aug  7 17:21:25 2013
{\small
\begin{tabular}{lllllllllllrrrrr}
  \hline
(Intercept) & PC1 & PC2 & PC3 & PC4 & PC5 & PC6 & PC7 & PC8 & PC9 & PC10 & df & logLik & AICc & delta & weight \\ 
  \hline
+ & + & + & + & + & + & + & + & + & + &  & 20.00 & -245.15 & 532.56 & 0.00 & 0.83 \\ 
  + & + & + & + & + & + & + & + & + & + & + & 22.00 & -244.53 & 535.79 & 3.23 & 0.17 \\ 
  + & + & + & + & + & + & + & + & + &  &  & 18.00 & -254.69 & 547.21 & 14.64 & 0.00 \\ 
  + & + & + & + & + & + & + & + &  &  &  & 16.00 & -258.00 & 549.45 & 16.88 & 0.00 \\ 
  + & + & + & + & + & + & + &  &  &  &  & 14.00 & -268.69 & 566.49 & 33.93 & 0.00 \\ 
  + & + & + & + & + & + &  &  &  &  &  & 12.00 & -271.30 & 567.42 & 34.86 & 0.00 \\ 
  + & + & + & + & + &  &  &  &  &  &  & 10.00 & -298.53 & 617.64 & 85.07 & 0.00 \\ 
  + & + & + & + &  &  &  &  &  &  &  & 8.00 & -314.50 & 645.37 & 112.81 & 0.00 \\ 
  + & + & + &  &  &  &  &  &  &  &  & 6.00 & -342.94 & 698.10 & 165.53 & 0.00 \\ 
  + & + &  &  &  &  &  &  &  &  &  & 4.00 & -349.55 & 707.20 & 174.64 & 0.00 \\ 
   \hline
\end{tabular}
}

@@

\begin{sidewaystable}
  \centering
% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Wed Aug  7 17:21:25 2013
{\small
\begin{tabular}{lllllllllllrrrrr}
  \hline
(Intercept) & PC1 & PC2 & PC3 & PC4 & PC5 & PC6 & PC7 & PC8 & PC9 & PC10 & df & logLik & AICc & delta & weight \\ 
  \hline
+ & + & + & + & + & + & + & + & + & + &  & 30.00 & -303.61 & 672.34 & 0.00 & 0.77 \\ 
  + & + & + & + & + & + & + & + & + & + & + & 33.00 & -301.25 & 674.74 & 2.41 & 0.23 \\ 
  + & + & + & + & + & + & + & + & + &  &  & 27.00 & -314.28 & 686.70 & 14.36 & 0.00 \\ 
  + & + & + & + & + & + & + & + &  &  &  & 24.00 & -318.22 & 687.70 & 15.37 & 0.00 \\ 
  + & + & + & + & + & + & + &  &  &  &  & 21.00 & -335.11 & 714.71 & 42.37 & 0.00 \\ 
  + & + & + & + & + & + &  &  &  &  &  & 18.00 & -353.04 & 743.91 & 71.57 & 0.00 \\ 
  + & + & + & + & + &  &  &  &  &  &  & 15.00 & -385.20 & 801.67 & 129.34 & 0.00 \\ 
  + & + & + & + &  &  &  &  &  &  &  & 12.00 & -397.69 & 820.21 & 147.87 & 0.00 \\ 
  + & + & + &  &  &  &  &  &  &  &  & 9.00 & -437.13 & 892.73 & 220.39 & 0.00 \\ 
  + & + &  &  &  &  &  &  &  &  &  & 6.00 & -451.19 & 914.60 & 242.27 & 0.00 \\ 
   \hline
\end{tabular}
}

@@

\begin{sidewaystable}
  \centering
% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Wed Aug  7 17:21:25 2013
{\small
\begin{tabular}{lllllllllllrrrrr}
  \hline
(Intercept) & PC1 & PC2 & PC3 & PC4 & PC5 & PC6 & PC7 & PC8 & PC9 & PC10 & df & logLik & AICc & delta & weight \\ 
  \hline
+ & + & + & + & + & + & + & + & + & + & + & 33.00 & -251.73 & 575.67 & 0.00 & 1.00 \\ 
  + & + & + & + & + & + & + & + & + & + &  & 30.00 & -268.54 & 602.18 & 26.51 & 0.00 \\ 
  + & + & + & + & + & + & + & + & + &  &  & 27.00 & -283.99 & 626.10 & 50.43 & 0.00 \\ 
  + & + & + & + & + & + & + & + &  &  &  & 24.00 & -295.61 & 642.46 & 66.78 & 0.00 \\ 
  + & + & + & + & + & + & + &  &  &  &  & 21.00 & -302.50 & 649.48 & 73.81 & 0.00 \\ 
  + & + & + & + & + & + &  &  &  &  &  & 18.00 & -316.59 & 671.00 & 95.32 & 0.00 \\ 
  + & + & + & + & + &  &  &  &  &  &  & 15.00 & -340.84 & 712.95 & 137.27 & 0.00 \\ 
  + & + & + & + &  &  &  &  &  &  &  & 12.00 & -353.01 & 730.84 & 155.17 & 0.00 \\ 
  + & + & + &  &  &  &  &  &  &  &  & 9.00 & -378.16 & 774.78 & 199.11 & 0.00 \\ 
  + & + &  &  &  &  &  &  &  &  &  & 6.00 & -395.71 & 803.64 & 227.97 & 0.00 \\ 
   \hline
\end{tabular}
}

@@

\begin{table}
  \centering
% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Wed Aug  7 17:21:25 2013
\begin{tabular}{r|rrrr}
  & morph 1 & morph 2 & molec 1 & molec 2 \\ 
  \hline
morph 1 &  &  &  &  \\ 
  morph 2 & 0.00 &  &  &  \\ 
  molec 1 & 0.00 & 0.00 &  &  \\ 
  molec 2 & 0.00 & 0.00 & 0.00 &  \\ 
   \hline
\end{tabular}

>>>>

\section{Results}
\subsection{Geometric morphometrics}
The results of the PCA of the total dataset of \textit{E. marmorata} pastral landmarks configurations demonstrates no clear or obvious groupings (Fig. \ref{fig:pca}). The first three PCs, which represent 45.29\% of the total variation, are a cloud of points with no structure. Additionally, individual landmark variation is mostly circular around each landmark with some more elliptical variation observed along some midline landmarks and the most lateral landmark (Fig. \ref{fig:pca}). However, it is important to note that Procustes based superimposition attempts to evenly distribute variance around the mean shape \citep{Zelditch2004} and this observation should be considered cursory at best.

The first two PCs appear to describe principally varaition in the lateral margin of te palstra, from a pointed medial edge to a more rounded and blunt edge (Fig. \ref{fig:pc_var}). Landmark 10 (Fig. \ref{fig:plastra}), which appears to be the most variable along these axes (Fig. \ref{fig:pca} and \ref{fig:pc_var}), is positioned on the bridge between the plastron and the carapace. Over ontogeny, this is an area that deepens dorsoventrally and when the plastron was projected into two dimensions this it created the effect of mediolateral movement.
Lateral landmark variation along the first PC seemed concentrated in the posterior portion of the plastra with additional variance observed in midline landmarks (Fig. \ref{fig:pc_var}). This variance in midline landmakrs was most likely caused by the fact that plastral scutes frequently do not line up perfectly. Along PC 2, lateral variation appeared to be concetrated in the anterior portion o the plastra (Fig. \ref{fig:pc_var}).

@@

% multinomial logistic regression model
The AICc best multinomial logistic regression model for three of the four classification schemes had the first 9 PCs as features (Tables \ref{tab:mod_sel_1}, \ref{tab:mod_sel_2}, and \ref{tab:mod_sel_3}). The second molecularly based classification hypothesis included all 10 possible PCs as predictors (Tables \ref{tab:mod_sel_4}).
The \(\Delta\)AICc values between the optimal and second best model range from 1.18 for the first morphological based classification hypothesis to 26.51 for the second molecular based classification hypothesis (Tables \ref{tab:mod_sel_1}, \ref{tab:mod_sel_2}, \ref{tab:mod_sel_3}, and \ref{tab:mod_sel_4}). The first 9 PCs describe 83.23\% of total variation in plastral shape, while the first 10 PCs describe 86.54\% of the variation.

While the \(\Delta\)AICc value between the optimal and second best model for the first morphological and first molecular based classification hypothesis was within the range to be considered equally optimal \citep{Burnham2002a}, for this analysis we chose to use only the AICc best model. While AICc values can not be compared between models with different responses \citep{Burnham2002a}, we interpret the fact that the \(\Delta\)AICc best model in these cases is the simpler model and that the optimal model for three of the classification schemes having the same number of predictors as reasons to use only the AICc best model for all cases. 
Additionally, by using a single model for each of the classification hypotheses, this limits the number of comparisons between the bootstrap resampled distributions of the AUC values for the testing dataset (see below).

@@

The selected number of features in the final random forest model for each classification scheme was very simplar to the model selection results from the multinomial logistic regression models, ranging from 9 for the second morphological based classification hypothesis and both molecular based classification hypotheses to 10 for the first morphological based classification hypothesis (Fig. \ref{fig:roc}).

@@

The first two most important features describe different aspects of variation (Fig. \ref{fig:imp_var}). The third and most important PC describes variation roundedness of the medial portion of the plastron, both the anterior and posterior portions of the plastron. Additionally, the relative position of the landmarks along the midline varies greatly along PC3 (Fig. \ref{fig:imp_var}). This PC represents 12.19\% of total variation. The second and second most important PC is described above and principally described variation in landmarks along the lateral and anterior margin of the plastron. This PC represents 12.78\% of total variation. The major variations along these axes correspond well to the differences between the mean shape of each class (Fig. \ref{fig:mean_shape}) where major class differences seem based on the relative ballooning or shrinking of the anterior and posterior portions of the plastron together along with differential ``pinching'' of the midline landmarks.

The relative risk values for classification from the multinomial logistic regression model, based on the three most important PCs, demonstrate that individual axes contribute to classification differently and that given multiple features the odds of determining the correct classification increase (Fig. \ref{fig:rel_risk}). The first most important axis contributes strongly to classifying both the western and southern groups while changes along the second most important axes contribute very little to increasing the odds of classification for all but the eastern group. This is observable from the class histograms of PC 3 and 2 (Fig. \ref{fig:imp_var}). Changes along the first and third most important axes contribute more obviously to increasing the odds of correctly identifying the class of an observation, a result that is observable in both the relative risk (Fig. \ref{fig:rel_risk}) and the different class histograms of the PCs (Fig. \ref{fig:imp_var}).

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width = \textwidth]{figure/pc_var}
  \caption{Landmark variation along the first two PCs of the Procrustes superimposed ``half'' plastral landmarks. The first row corresponds to variation along the first PC, while the second row corresponds to the second PC. The left most column represents the observation with the highest eigenscore along that PC, while the right most column represents the observation with the lowest eigenscore. The middle column, for both rows, is the mean plastral shape for all observations. The first PC represents 20.32\% of the total variation in plastral shape while PC represents 12.78\% of the variance.}
  \label{fig:pc_var}
\end{figure}

@@

\begin{sidewaystable}
  \centering
% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Thu Aug  8 00:20:39 2013
{\small
\begin{tabular}{lllllllllllrrrrr}
  \hline
(Intercept) & PC1 & PC2 & PC3 & PC4 & PC5 & PC6 & PC7 & PC8 & PC9 & PC10 & df & logLik & AICc & delta & weight \\ 
  \hline
+ & + & + & + & + & + & + & + & + & + &  & 20.00 & -250.00 & 542.26 & 0.00 & 0.64 \\ 
  + & + & + & + & + & + & + & + & + & + & + & 22.00 & -248.35 & 543.43 & 1.18 & 0.36 \\ 
  + & + & + & + & + & + & + & + &  &  &  & 16.00 & -261.94 & 557.33 & 15.07 & 0.00 \\ 
  + & + & + & + & + & + & + & + & + &  &  & 18.00 & -259.99 & 557.82 & 15.56 & 0.00 \\ 
  + & + & + & + & + & + & + &  &  &  &  & 14.00 & -275.68 & 580.48 & 38.22 & 0.00 \\ 
  + & + & + & + & + & + &  &  &  &  &  & 12.00 & -281.10 & 587.03 & 44.77 & 0.00 \\ 
  + & + & + & + & + &  &  &  &  &  &  & 10.00 & -305.55 & 631.68 & 89.43 & 0.00 \\ 
  + & + & + & + &  &  &  &  &  &  &  & 8.00 & -318.48 & 653.34 & 111.09 & 0.00 \\ 
  + & + & + &  &  &  &  &  &  &  &  & 6.00 & -344.14 & 700.49 & 158.24 & 0.00 \\ 
  + & + &  &  &  &  &  &  &  &  &  & 4.00 & -346.80 & 701.71 & 159.45 & 0.00 \\ 
   \hline
\end{tabular}
}

@@

\begin{sidewaystable}
  \centering
% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Thu Aug  8 00:20:39 2013
{\small
\begin{tabular}{lllllllllllrrrrr}
  \hline
(Intercept) & PC1 & PC2 & PC3 & PC4 & PC5 & PC6 & PC7 & PC8 & PC9 & PC10 & df & logLik & AICc & delta & weight \\ 
  \hline
+ & + & + & + & + & + & + & + & + & + &  & 20.00 & -245.15 & 532.56 & 0.00 & 0.83 \\ 
  + & + & + & + & + & + & + & + & + & + & + & 22.00 & -244.53 & 535.79 & 3.23 & 0.17 \\ 
  + & + & + & + & + & + & + & + & + &  &  & 18.00 & -254.69 & 547.21 & 14.64 & 0.00 \\ 
  + & + & + & + & + & + & + & + &  &  &  & 16.00 & -258.00 & 549.45 & 16.88 & 0.00 \\ 
  + & + & + & + & + & + & + &  &  &  &  & 14.00 & -268.69 & 566.49 & 33.93 & 0.00 \\ 
  + & + & + & + & + & + &  &  &  &  &  & 12.00 & -271.30 & 567.42 & 34.86 & 0.00 \\ 
  + & + & + & + & + &  &  &  &  &  &  & 10.00 & -298.53 & 617.64 & 85.07 & 0.00 \\ 
  + & + & + & + &  &  &  &  &  &  &  & 8.00 & -314.50 & 645.37 & 112.81 & 0.00 \\ 
  + & + & + &  &  &  &  &  &  &  &  & 6.00 & -342.94 & 698.10 & 165.53 & 0.00 \\ 
  + & + &  &  &  &  &  &  &  &  &  & 4.00 & -349.55 & 707.20 & 174.64 & 0.00 \\ 
   \hline
\end{tabular}
}

@@

\begin{sidewaystable}
  \centering
% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Thu Aug  8 00:20:39 2013
{\small
\begin{tabular}{lllllllllllrrrrr}
  \hline
(Intercept) & PC1 & PC2 & PC3 & PC4 & PC5 & PC6 & PC7 & PC8 & PC9 & PC10 & df & logLik & AICc & delta & weight \\ 
  \hline
+ & + & + & + & + & + & + & + & + & + &  & 30.00 & -303.61 & 672.34 & 0.00 & 0.77 \\ 
  + & + & + & + & + & + & + & + & + & + & + & 33.00 & -301.25 & 674.74 & 2.41 & 0.23 \\ 
  + & + & + & + & + & + & + & + & + &  &  & 27.00 & -314.28 & 686.70 & 14.36 & 0.00 \\ 
  + & + & + & + & + & + & + & + &  &  &  & 24.00 & -318.22 & 687.70 & 15.37 & 0.00 \\ 
  + & + & + & + & + & + & + &  &  &  &  & 21.00 & -335.11 & 714.71 & 42.37 & 0.00 \\ 
  + & + & + & + & + & + &  &  &  &  &  & 18.00 & -353.04 & 743.91 & 71.57 & 0.00 \\ 
  + & + & + & + & + &  &  &  &  &  &  & 15.00 & -385.20 & 801.67 & 129.34 & 0.00 \\ 
  + & + & + & + &  &  &  &  &  &  &  & 12.00 & -397.69 & 820.21 & 147.87 & 0.00 \\ 
  + & + & + &  &  &  &  &  &  &  &  & 9.00 & -437.13 & 892.73 & 220.39 & 0.00 \\ 
  + & + &  &  &  &  &  &  &  &  &  & 6.00 & -451.19 & 914.60 & 242.27 & 0.00 \\ 
   \hline
\end{tabular}
}

@@

\begin{sidewaystable}
  \centering
% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Thu Aug  8 00:20:39 2013
{\small
\begin{tabular}{lllllllllllrrrrr}
  \hline
(Intercept) & PC1 & PC2 & PC3 & PC4 & PC5 & PC6 & PC7 & PC8 & PC9 & PC10 & df & logLik & AICc & delta & weight \\ 
  \hline
+ & + & + & + & + & + & + & + & + & + & + & 33.00 & -251.73 & 575.67 & 0.00 & 1.00 \\ 
  + & + & + & + & + & + & + & + & + & + &  & 30.00 & -268.54 & 602.18 & 26.51 & 0.00 \\ 
  + & + & + & + & + & + & + & + & + &  &  & 27.00 & -283.99 & 626.10 & 50.43 & 0.00 \\ 
  + & + & + & + & + & + & + & + &  &  &  & 24.00 & -295.61 & 642.46 & 66.78 & 0.00 \\ 
  + & + & + & + & + & + & + &  &  &  &  & 21.00 & -302.50 & 649.48 & 73.81 & 0.00 \\ 
  + & + & + & + & + & + &  &  &  &  &  & 18.00 & -316.59 & 671.00 & 95.32 & 0.00 \\ 
  + & + & + & + & + &  &  &  &  &  &  & 15.00 & -340.84 & 712.95 & 137.27 & 0.00 \\ 
  + & + & + & + &  &  &  &  &  &  &  & 12.00 & -353.01 & 730.84 & 155.17 & 0.00 \\ 
  + & + & + &  &  &  &  &  &  &  &  & 9.00 & -378.16 & 774.78 & 199.11 & 0.00 \\ 
  + & + &  &  &  &  &  &  &  &  &  & 6.00 & -395.71 & 803.64 & 227.97 & 0.00 \\ 
   \hline
\end{tabular}
}

@@

\begin{table}
  \centering
% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Thu Aug  8 00:20:39 2013
\begin{tabular}{r|rrrr}
  & morph 1 & morph 2 & molec 1 & molec 2 \\ 
  \hline
morph 1 &  &  &  &  \\ 
  morph 2 & 0.00 &  &  &  \\ 
  molec 1 & 0.00 & 0.00 &  &  \\ 
  molec 2 & 0.00 & 0.00 & 0.00 &  \\ 
   \hline
\end{tabular}
